On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-16 main.tex
minor fix

\begin{lemma}\label{thm:dead-construction-greedy-bisim}
    Given any eager bisimulation \({≈} ⊆ S × U\) with the underlying bisimulation \({∼}\), the following relation \({∼_d} ⊆ S × U\):
    \[{∼_d} ≜ {∼} ∪ \{(s, u) ∣ \text{\(s\) and \(u\) are dead in \(S\) and \(U\)}\},\]
    form a GKAT coalgebra the transition function \(δ_≈\) in~\Cref{def:norm-bisim}, which implies \({≈} ⊑ \)
    Furthermore, \(\norm(∼_d)\) is a bisimulation between \(\norm(S)\) and \(\norm(U)\).
\end{lemma}

@@

\begin{theorem}\label{thm:greedy-bisim-one-dead}

\end{theorem}

>>>>

\begin{lemma}\label{thm:dead-construction-greedy-bisim}
    Given any eager bisimulation \({≈} ⊆ S × U\) with the underlying bisimulation \({∼}\), the following relation \({∼_d} ⊆ S × U\):
    \[{∼_d} ≜ {∼} ∪ \{(s, u) ∣ \text{\(s\) and \(u\) are dead in \(S\) and \(U\)}\},\]
    form a GKAT coalgebra the transition function \(δ_≈\) in~\Cref{def:norm-bisim}, which implies \({≈} ⊑ {∼_d}\).
    Furthermore, \(\norm(∼_d)\) is a bisimulation between \(\norm(S)\) and \(\norm(U)\).
\end{lemma}

@@

\begin{theorem}\label{thm:greedy-bisim-one-dead}
    Consider two states in GKAT coalgebras \(s ∈ S, u ∈ U\) and an arbitrary bisimulation \(≈\), if \(s\) is dead, then 
    \begin{itemize}
        \item if \(u\) is not dead, then \((s, u) ∉ {≈}\).
        \item if \(u\) is dead, 
    \end{itemize}
\end{theorem}
